\documentclass[../../main/main.tex]{subfiles}
\begin{document}
\section{Solving LCP}

Before diving into a solution for the Nash equilibrium of LCP, we first address the uniqueness of such a solution. LCP has an infinite class of Nash equilibria, differentiated only by how the bettor sizes their bluffing hands. In this section, we define a way to distinguish between these equilibria. This involves two steps: first, defining a class of \textit{monotone} calling strategies which are, in some sense, more reasonable than non-monotone strategies; and second, restricting the bettor's strategy to be admissible (not weakly dominated) against these calling strategies. This turns out to be enough to uniquely determine the Nash equilibrium.

\subsection{Monotone Strategies}

\begin{definition}[Monotone Calling Strategy]
    A calling strategy is \textit{monotone} if it satisfies two conditions:
    \begin{enumerate}
        \item For any bet size $s$ and any two hand strengths $y_1 < y_2$, if the caller calls a bet of size $s$ with $y_1$, they must also call with $y_2$.
        \item For any hand strength $y$ and any two bet sizes $s_1 < s_2$, if the caller calls a bet of size $s_2$ with $y$, they must also call a bet of size $s_1$ with $y$.
    \end{enumerate}
\end{definition}

This should sound intuitive. Clearly, calling with a stronger hand is weakly better than calling with a weaker hand. Violating the first condition (in a non-negligible way) is actually weakly dominated - not only is a monotone strategy weakly better against all opponents, but there exists an opponent against which the non-monotone strategy is strictly better. We prove this in lemma \ref{lem:monotone_dominated}.

\begin{lemma}
    \label{lem:monotone_dominated}
    If a calling strategy violates the first monotonicity condition for a nonzero-measure set of hands for any bet size $s$, it is weakly dominated. Specifically, if there exists $s$ and sets $A, B \subseteq [0, 1]$ such that:
    \begin{enumerate}
        \item The caller calls $s$ with hands in $A$
        \item The caller folds $s$ with hands in $B$
        \item $\sup A \leq \inf B$
        \item $A$ and $B$ have positive measure
    \end{enumerate}
    then the strategy is weakly dominated.
\end{lemma}
\begin{proof}
    Let $\sigma_C$ be the non-monotone strategy described above. Since $A$ and $B$ are nonzero-measure, there exist subsets $A' \subseteq A$ and $B' \subseteq B$ such that:
    \begin{enumerate}
        \item $A'$ and $B'$ have positive measure
        \item $|A'| = |B'|$
    \end{enumerate}
    Let $\sigma_C'$ be the strategy which switches the actions for $A'$ and $B'$, i.e. calls with $B'$ and folds with $A'$ (and behaves equivalently for all other bet sizes). Against a bet of size $s$, whenever $y \in B'$ and $x \in A'$, $\sigma_C$ folds while $\sigma_C'$ calls and wins. Similarly, whenever $y \in A'$ and $x \in B'$, $\sigma_C$ calls and loses while $\sigma_C'$ folds. For all other cases, $\sigma_C$ and $\sigma_C'$ behave identically. This means that $\sigma_C'$ is weakly better than $\sigma_C$ against every betting strategy. Now consider a betting strategy which always bets $s$. Against this strategy, both cases above occur with positive probability, so $\sigma_C'$ is strictly better than $\sigma_C$. Thus, $\sigma_C$ is weakly dominated.
\end{proof}

The second condition for a monotone calling strategy - that the caller must be more willing to call smaller bets - is more subtle. From a poker player's perspective, it aligns with intuition about pot odds - a larger bet is more risky, so it should require a stronger hand to call. 
However, violating this condition is not dominated - in fact, it is common in real poker. Often, a larger bet is perceived as a bluff while a smaller bet is perceived as a value bet. Whether or not it is optimal, a caller might call more aggressively against large bets based on this perception.
To motivate this condition from more fundamental game-theoretic principles, we consider how it affects the bettor's response. If the caller violates this condition by calling less aggressively against smaller bets, then the bettor gets away with taking smaller risks for higher returns. Because of this, a monotone calling strategy is less exploitable. Imposing this condition on the caller restricts the betting strategies in a way that gives us a unique Nash equilibrium.

\begin{definition}[Monotone-Admissible Strategy]
    A betting strategy $\sigma_B$ is \textit{monotone-admissible} if it is admissible in LCP against the set of monotone calling strategies. More explicitly, $\sigma_B$ is monotone-admissible if there does not exist a betting strategy $\sigma_B'$ such that both of the following hold:
    \begin{enumerate}
        \item $\pi_B(\sigma_B',\sigma_C) \geq \pi_B(\sigma_B,\sigma_C)$ for all monotone calling strategies $\sigma_C$
        \item $\pi_B(\sigma_B',\sigma_C) > \pi_B(\sigma_B,\sigma_C)$ for at least one monotone calling strategy $\sigma_C$
    \end{enumerate}
\end{definition}

This is useful in distinguishing bettor strategies which differ only in how they bluff. We will see that the hand strength of a bluff is irrelevant if the caller plays optimally because the caller will never call with a hand weaker than any bluff. However, if the caller deviates to a suboptimal but still monotone strategy, then the bettor's bluffing hand strength becomes important. If the caller becomes too loose, i.e. calling too often with weak hands, then the bettor ends up winning some pots ``accidentally" if they make their smallest bluffs with their strongest bluffing hands. This is where monotone-admissibility differentiates between equilibria.

\subsection{Nash Equilibrium Structure}

We will now describe the structure of the Nash equilibrium in terms of constants $x_i$ and functions $c(s)$, $b(s)$, and $v(s)$. These turn out to be fully determined by the parameters $L$ and $U$, but for now they are unknown. Notice that both players use pure strategies, like in NLCP: the bettor maps hand strengths directly to bet sizes, and the caller maps hand strengths and bet sizes to actions with no mixing.

    \begin{enumerate}
        \item The caller has a calling threshold $c(s)$ that is continuous in $s$, including at endpoints $L$ and $U$. They call with hands $y \geq c(s)$ and fold with hands $y < c(s)$\footnote{The action taken at the threshold is irrelevant, since it occurs with probability zero.}.
        \item The bettor partitions $[0,1]$ into three regions: bluffing $x \in [0,x_2]$, checking $x \in [x_2,x_3]$, and value betting $x \in [x_3,1]$.
        \item Within the bluffing region, the bettor's partitions into a max-betting region $x \in [x_0,x_1]$, an intermediate region $x \in [x_1,x_2]$, and a min-betting region $x \in [x_2,x_3]$.
        \item Within the intermediate bluffing region, the bettor bets according to a continuous, decreasing function $s=b^{-1}(x)$ with endpoints $b^{-1}(x_0)=U$ and $b^{-1}(x_3)=L$.
        \item Within the value betting region, the bettor partitions into a min-betting region $x \in [x_3,x_4]$, an intermediate region $x \in [x_4,x_5]$, and a max-betting region $x \in [x_5,1]$.
        \item Within the intermediate value betting region, the bettor bets according to a continuous, increasing function $s=v^{-1}(x)$ with endpoints $v^{-1}(x_3)=L$ and $v^{-1}(x_5)=U$.
    \end{enumerate}



% \begin{customproof}
%     We will prove the structure of the Nash equilibrium by establishing each claim:
%     % \begin{enumerate}
%     %     \item The caller must use a threshold strategy with cutoff $c(s)$
%     %     \item The cutoff $c(s)$ must be continuous, even at endpoints $L$ and $U$
%     %     \item The bettor must bet for value with hands stronger than $c(s)$, bluff with hands weaker than $c(s)$, and check some range of intermediate hands
%     %     \item Value betting sizes must increase with hand strength
%     %     \item When bluffing, the bettor must be indifferent among exactly the sizes which are used for value betting
%     %     \item Bluffing sizes should decrease with hand strength
%     % \end{enumerate}

%     \textbf{Claim 1:} The caller must use a threshold strategy with cutoff $c(s)$. This follows from lemma \ref{lem:monotone_dominated}.

%     % \textbf{Claim 2:} The cutoff $c(s)$ must be non-decreasing in $s$.
%     % If $c(s)$ were decreasing at any point, the bettor could exploit this by bluffing with a slightly smaller size than they would otherwise use. This would cause the caller to fold more often while risking less money, contradicting equilibrium.

%     \textbf{Claim 2:} The cutoff $c(s)$ must be continuous, even at endpoints $L$ and $U$.
%     If $c(s)$ had a discontinuity, the bettor's expected value from bluffing would also be discontinuous. They could then exploit by bluffing with sizes just below the discontinuity, contradicting equilibrium.

%     \textbf{Claim 3:} Value bets must be made with hands stronger than $c(s)$, bluffs with hands weaker than $c(s)$.
%     By definition, when value betting size $s$, the bettor wants to get called by weaker hands (requiring $x > c(s)$). When bluffing size $s$, the bettor wants to get called by stronger hands (requiring $x < c(s)$).

%     \textbf{Claim 4:} Value betting sizes must increase with hand strength.
%     Since $c(s)$ is non-decreasing, stronger hands can profitably bet larger sizes and get called by a more restricted range of strong hands. Weaker value betting hands must bet smaller to get called by a wider range.

%     \textbf{Claim 5:} The bettor must be indifferent among bluffing sizes that are also used for value bets.
%     The expected value of bluffing size $s$ is:
%     \begin{equation}
%         \mathbb{E}[\text{bluff } s] = c(s) - (1-c(s)) \cdot s
%     \end{equation}
%     This is independent of the bettor's hand strength. If the bettor strictly preferred certain sizes for bluffing, they would never bluff with other sizes. If any other size were used for value betting, then the caller could exploit by only calling those sizes with hands stronger than the value betting range.
%     Additionally, the bettor cannot bluff with sizes which are not used for value betting. In this case, the caller can similarly exploit by always calling this size with hands stronger than the bluffing range.

%     \textbf{Claim 6:} Bluffing sizes should decrease with hand strength. This claim is not necessary to have a Nash equilibrium, but it is what makes the bettor's strategy monotone-admissible.
%     If the caller deviates by calling too loosely but maintains consistency (never calling with weaker hands and folding with stronger hands to the same bet size), the bettor uniquely benefits by bluffing larger with their weakest hands and bluffing smaller with their strongest hands. This gives them a possibility of winning showdowns with their strongest bluffing hands, which would not happen if they bluffed large with the strongest hands.
%     \todo{admissiblity?}
% \end{customproof}

See figure \ref{fig:strategyprofile} for visual representations of the strategy profile. 

\subsection{Constraints and Indifference Equations}

The Nash equilibrium strategy profile must satisfy several constraints and indifference conditions, which we will derive and use to solve for the strategy profile. The key conditions are:

\begin{itemize}
    \item The caller must be indifferent between calling and folding at their calling threshold
    \item The bettor must be indifferent between checking and betting at their value betting and bluffing thresholds
    \item The bettor's bet size for a value bet must maximize their expected value
    \item The bettor's strategy must be continuous in bet size (in the regions where they bet)
\end{itemize}

These conditions give us the following system of equations:

\begin{align*}
    \text{Caller Indifference:} & \\
    & (x_4-x_3) \cdot (1+L) - (x_2-x_1) \cdot L = 0\\
    & (1-x_5) \cdot (1+U) - x_0 \cdot U = 0\\
    & |b'(s)| \cdot (1 + s) + |v'(s)| \cdot s = 0\\
    \text{Bettor Indifference and Optimality:} & \\
    & -sc'(s) - c(s) + 2 v(s) - 1 = 0\\
    & c(L) - (1-c(L)) \cdot L = x_3\\
    & c(s) - (1-c(s)) \cdot s = x_2\\
    \text{Continuity Constraints:} & \\
    & b(U) = x_0 \\
    & b(L) = x_1 \\
    & v(U) = x_5 \\
    & v(L) = x_4
\end{align*}

We will now derive each of these equations in turn.

\subsubsection{Caller Indifference}
\label{subsec:caller_indifference}

By definition, $c(s)$ is the threshold above which the caller calls and below which they fold. This means that in Nash Equilibrium, the caller must be indifferent between calling and folding with a hand strength of $c(s)$:


  \[  \mathbb{E}[\text{call } c(s)] = \mathbb{E}[\text{fold } c(s)] \]
  \[  \mathbb{P}[\text{bluff} | s] \cdot (1+s) - \mathbb{P}[\text{value bet} | s]\cdot s = 0 \]


We now split into cases based on the value of $s$.

\textbf{Case 1: $s = L$}. The hands the bettor value bets $L$ with are $x \in (x_3, x_4)$, and the hands they bluff with are $x \in (x_1, x_2)$. 

\begin{equation}{\label{callindiffmin}}
    (x_4-x_3) \cdot (1+L) - (x_2-x_1) \cdot L = 0
\end{equation}

\textbf{Case 2: $s = U$}. The hands the bettor value bets $U$ with are $x \in (x_5, 1)$, and the hands they bluff with are $x \in (0, x_0)$. 

\begin{equation}{\label{callindiffmax}}
    (1-x_5) \cdot (1+U) - x_0 \cdot U = 0
\end{equation}

\textbf{Case 3: $L \leq s \leq U$}. In this case, the bettor has exactly one value hand and one bluffing hand, but somewhat paradoxically, they are not equally likely. The probability of a value bet given the size $s$ is related to the inverse derivative of the value function $v(s)$ at $s$, and the same goes for a bluff. This gives us the following relation:

\[ \frac{\mathbb{P}[\text{value bet} | s]}{\mathbb{P}[\text{bluff} | s]} = \frac{|b'(s)|}{|v'(s)|}\]

An intuitive interpretation of this is that for any small neighborhood around the bet size $s$, the bettor has more hands which use a bet size in the neighborhood if $v(s)$ does not change rapidly around $s$, that is, if $|v'(s)|$ is small. The same goes for bluffing hands, and as we limit the neighborhood to a single point, the ratio of the two probabilities approaches the ratio of the derivatives. Plugging this into the indifference equation, we get:

\begin{equation}{\label{callindiff}}
    |b'(s)| \cdot (1 + s) + |v'(s)| \cdot s = 0
\end{equation}

\subsubsection{Bettor Indifference and Optimality}

When the bettor makes a value bet, they are attempting to maximize the expected value of the bet. We can write the expected value of a value bet as:

\begin{align*}
    \mathbb{E}[\text{value bet } s | x] & = \mathbb{P}[\text{call with worse}] \cdot (1+s) - \mathbb{P}[\text{call with better}] \cdot s + \mathbb{P}[\text{fold}] \cdot 1 \\
    & = (x-c(s)) \cdot (1+s) - (1-x) \cdot (s) + c(s)\\
\end{align*}

To maximize this, we take the derivative with respect to $s$ and set it equal to zero. Crucially, we are treating $c(s)$ as a function of $s$ and using the chain rule, since changing the bet size $s$ will also change the calling threshold $c(s)$. We want this optimality condition to hold for the bettor's Nash equilibrium strategy, so we set $x=v(s)$. This gives us:

\begin{align}{\label{valueoptimality}}
    \nonumber \frac{d}{ds} \mathbb{E}[\text{value bet } s | x=v(s)] & = 0 \\
    -sc'(s) - c(s) + 2 v(s) - 1 & = 0
\end{align}

Additionally, when the bettor has the most marginal value betting hand at $x=x_3$, they should be indifferent between a minimum value bet and a check: 

\begin{align}{\label{valueindiff}}
    \nonumber \mathbb{E}[\text{value bet } L | x=x_3] & = \mathbb{E}[\text{check} | x=x_3]\\ 
    (x_3-c(L)) \cdot (1+L) - (1-x_3) \cdot (L) + c(L) & = x_3
\end{align}

Finally, when the bettor has the most marginal bluffing hand at $x=x_2$, they should be indifferent between a minimum bluff and a check. However, as we discussed earlier, the bettor should be indifferent among all bluffing sizes, so the bettor should actually be indifferent between checking and making any bluffing size $s$ at $x=x_2$. This gives us:

\begin{align}{\label{bluffindiff}}
    \nonumber \mathbb{E}[\text{bluff } s | x=x_2] & = \mathbb{E}[\text{check} | x=x_2]\\ 
    c(s) - (1-c(s)) \cdot s & = x_2
\end{align}

\subsubsection{Continuity Constraints}

As discussed above, the bettor's strategy is continuous in $s$ and $x$ (except when checking). This means that the endpoints of the functions $v(s)$ and $b(s)$ are constrained as follows:

\begin{equation}{\label{continuityconstraints}}
	 b(U) = x_0, \;\; b(L) = x_1, \;\; v(U) = x_5, \;\; v(L) = x_4
\end{equation}

\end{document}